### 2014-11-07 evaluation.tex
Minor edit to evaluation

Figure~\ref{grf:rubis} compares the \name implementation of RUBiS in a
\cf{1DC} configuration against a single replica ({\sf NoRep}) and a strongly
replicated ({\sf StrongRep}) \cf{1DC} deployment. The benchmark uses the
default RUBiS bidding mix, which has 15\% read-write interactions, which is
representative of the auction workload.  Without replication, {\sf NoRep}
trivially provides strong consistency. However, this deployment does not
scale beyond 1750 operations per second. Strong replication offers better
throughput at the cost of greater latency due to inter-replica
coordination. The \name deployment offers the benefit of replication, while
only paying the cost of coordination when necessary.

>>>>

Figure~\ref{grf:rubis} compares the \name implementation of RUBiS in a
\cf{1DC} configuration against a single replica ({\sf\small NoRep}) and a strongly
replicated ({\sf\small StrongRep}) \cf{1DC} deployment. The benchmark uses the
default RUBiS bidding mix, which has 15\% read-write interactions, which is
representative of the auction workload.  Without replication, {\sf\small NoRep}
trivially provides strong consistency. However, this deployment does not
scale beyond 1750 operations per second. Strong replication offers better
throughput at the cost of greater latency due to inter-replica
coordination. The \name deployment offers the benefit of replication, while
only paying the cost of coordination when necessary.
